\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-31 article/main.tex

% Need result table

@@

\subsection{Language dependance}

@@

\subsection{Detection Level}

>>>>

@@

\subsection{Language dependance}
The majority of techniques are language dependant and the most used 
languages are Java and C++

But those detection methods can be easily converted to other languages
just by modifying the font-end.

@@

\subsection{Detection Level}
We found out that almost all of design patterns detection methods 
identify the patterns on a source code level, though, the detection could
be done on multiple levels.
